Modeling potential JCPOA diversion scenarios using Cyclus

### 2018-01-27 paper.tex
adding paper.pdf

The Joint Comprehensive Plan of Action (JCPOA)\cite{jcpoa} %cite JCPOA agreement
limits the Iranian nuclear program and, in return, lifts many of the economic
sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
limited in its ability to enrich uranium. This paper presents a model to probe
the enriching ability of various cascade configurations that are related to
JCPOA agreement limits. The analysis was performed using the Cyclus fuel cycle
\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
simulation framework in order to demonstrate that such analysis can be
integrated into a fuel cycle with material flowing among multiple facilities.

>>>>

The Joint Comprehensive Plan of Action (JCPOA)\cite{jcpoa} %cite JCPOA agreement
limits the Iranian nuclear program and, in return, lifts many of the economic
sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
limited in its ability to enrich uranium. This paper presents a model to probe
the enriching ability of various cascade configurations that are related to
JCPOA agreement limits. The analysis was performed using the Cyclus fuel cycle
\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
simulation simulator in order to demonstrate that such analysis can be
integrated into a fuel cycle with material flowing among multiple facilities.
